Alleviating the Topology Mismatch Problem in Distributed Overlay Networks

### 2014-02-02 unstructured.tex
2013.07.28 (Vassilis) Further investigation conducted to find research work that references the papers/algorithms we survey and cite. Text enriched.

The \emph{directed BFS}
tries to avoid the aforementioned delay by forwarding 
query messages only to a selected subset of available neighbors. The selection
criteria varies, from the number of results received previously or the distance
in terms of hops traveled to locate these results, to the bandwidth, or the
query load of the neighbor. That way, fewer nodes are visited but quality of
query responses is maintained, to a large degree, on the premise that the
selected heuristics can direct the search to the right path.
%
In \emph{local indices},
each node indexes data within a radius of $r$ hops and uses 
this local index to answer queries % on behalf of them 
without generating additional traffic. Local indices
greatly reduce the aggregate bandwidth usage of the network and 
improve query efficiency. However, updating such indices in 
the presence of frequent node joins/departures 
may introduce significant overhead should the radius is kept broad.
%%
Below, we outline how the techniques in~\cite{YG-M2002}
fare against the $3$ major performance criteria 
of Section~\ref{section:background}.
% \begin{center}
% \begin{tabular}{ccc}
% \textbf{Efficiency} & \textbf{Overhead} & \textbf{Scalability} \\
% \hline
% Iterative Deepening & ? & ? & ?
% Directed BFS & ? & ? & ?
% Local Indices & ? & ? & ?
% \end{tabular}
% \end{center}
\begin{center}
{\footnotesize
\begin{tabular}{rccc}
\multicolumn{1}{r}{} &
\multicolumn{1}{c}{\emph{Efficiency}} &
\multicolumn{1}{c}{\emph{Overhead}} &
\multicolumn{1}{c}{\emph{Scalability}}
\\
\cline{2-4}
\emph{Iterative Deepening} &
% needs recalculation in every iteration step
% extra delay imposed in a high churn environment that prohibits the algorithm
% to start from the last level of nodes and results in a restart of the whole
% process
low &
% the process in not started from the beginning at each iteration step
low &
% 
medium \\
\emph{Directed BFS} &
% Better time to satisfaction compared to iterative deepening
medium &
% Better quality and quicker results mean more aggregate bandwidth and
% processing power needs to be consumed since more nodes are involved (death
% spiral).
medium &
% BFS is Gnutella's non efficient communication method
medium \\
\emph{Local Indices} &
% efficiency is enhanced greatly since data pointers are replicated across the
% network
high &
% updating indices is a time and resource consuming process.
medium &
% the scalability is constrained by the indices update in a highly dynamic
% environment (high churn)
medium \\
\end{tabular}
}
\end{center}

@@

The key objective of the {\sl Gia} system~\cite{CRBLS2003} is 
to help alleviate the scalability omnipresent
in unstructured \p\ file-sharing systems.
At first, {\sl Gia} replaced {\sl Gnutella}'s blind flooding 
with random walks.
Although this adoption was 
a step in the right direction~\cite{lv_randomwalks_2002},
issuing a single copy of the query within the network
effectively reduces the search scope and may negatively affect 
the success rate of the query in question.
To overcome this limitation, {\sl Gia} introduces
a token-based flow control mechanism 
that gradually redirects queries to nodes which are more
likely to answer. This flow control mechanism also helps prevent node
overloading as each peer ``announces'' the number of query requests it 
can handle, in terms of tokens, to its neighbors; to this end, 
peers only forward query requests to nodes that they previously
received tokens from. Further refinement to the search mechanism is the
support for \emph{one--hop replication} of pointers to content.
{\sl Gia} also acknowledges the heterogeneity in peer bandwidth,
processing power, disk speed, etc., of \p\ nodes and uses this
information when connecting nodes to each other.
By using a topology adaptation algorithm, 
{\sl Gia} places low capacity nodes within 
short proximity to peers with high performance features.
This topology adaptation algorithm is based on the metric 
each node maintains about its satisfaction --ranging between $0$ and $1$--
for the neighbors it finds itself associated with. 
Through message exchange, a peer can establish new connections 
or drop superseded ones in order to improve its satisfaction.
Despite the fact that {\sl Gia}'s topology adaptation algorithm 
that primarily focuses on the satisfaction of peers improves the network's 
scalability, it falls short in addressing the mismatch problem
as considerations for the underlying network are not handled in explicit
terms.
%
In terms of the $3$ stated criteria, {\sl Gia}'s approach is as follows:
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Reduces the search scope.
medium &
% Only one copy of the query is issued to the network.
% A token based flow control mechanism redirects queries to nodes that are most
% likely to fulfill them.
low &
% Even thought the low overhead scalability is reduced by the reducing of
% search scope.
medium
\end{tabular}
}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{Distributed Cycle Minimization Protocol (DCMP)}
Another problem with topology unaware
systems is the duplication of messages due to cycles in the network graph.
Interestingly, such cycles appear even along the correct forwarding path.
\cite{ZKB2008}~focuses on this exact deficiency of overlay networks and
introduces the \emph{Distributed Cycle Minimization Protocol
(DCMP)}, a dynamic, fully distributed method that removes cycles;
this is accomplished without sacrificing
overlay connectivity, resilience and other key properties of unstructured
\p\ architectures and by avoiding a hierarchical organization of peers. 
Once a cycle is detected in {\it DCMP}, the most powerful node in that cycle 
is elected as the \emph{Gate Peer} and the cycle is then broken in that place
that it will result in the minimization of the distance between the
\emph{Gate Peer} and all other nodes that are currently part of the cycle. 
This process is managed by using two specialized message types 
namely, \emph{Information Collection Message (ICM)} and \emph{Cut Message (CM)}. 
\emph{DCMP} bases its operation on messages whose travel is limited by an
imposed $TTL$ value (max set to $7$ for most cases). This inherently limits
the protocol in detecting cycles that span for more than $TTL$ nodes.
Even though cycle elimination does improve network performance, 
it cannot  directly contribute in the solution of the topology mismatch problem.
%
%\begin{figure}
%\centering
%  \includegraphics[scale=0.4]{img/dcmp.jpeg}
%\caption{Cycle elimination methods in DCMP}
%\label{figure:dcmp}
%\end{figure}
%
% TODO: SOME DISCUSSION
%Actually, the duplicate packet problem seems to hurt more the active nodes;
%those with higher capacities and bandwidth that contribute the most to the
%network.
The expected \emph{DCMP} behavior as far as our $3$ criteria is:
%
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% It returns more result than LTM according to experiments in
% \cite{ZKB2008}
medium &
% Duplicates are an important fraction of the redundant overhead imposed by
% topology mismatch and thus DCMP minimizes this as possible.
% The control overhead is also one to two orders of magnitude less than LTM due
% to its ``lazy'' broadcasting of control messages (as opposed to LTM's periodic
% approach) - \cite{ZKB2008}
low &
% fully distributed method
high
\end{tabular}
}
\end{center}

@@

In~\cite{CS2002}, replication is used as a way to improve inefficient blind
search. As the number of replicas and/or cached copies increases in the network,
it would relatively easy to locate items even if search is random.
To analyze the feasibility of such an approach, \cite{CS2002} investigates
$3$ replication strategies: \emph{uniform}, \emph{proportional}, and
\emph{square root allocation}. In the uniform model, the copies of items are
uniformly spread over the network, while in the proportional, items are
replicated based on their query rate, so that frequently queried items can be
found more often.
The square root is a compromise between uniform and proportional allocation
models. The overall costs for both successful and unsuccessful
searches are compared to ascertain the effectiveness of the $3$ suggested 
approaches. Experimental outcomes indicate that the uniform allocation 
minimizes the maximum search length and so it can reduce the time spent on
unsuccessful searches. 
The proportional strategy effectively decreases the search time 
for popular items, but suffers when needing to locate the rare entities.
When it comes to expected successful search size, it is the same for 
for both uniform and proportional models and any approach in between 
to always behave much better. The square root allocation  aims at minimizing the 
expected search size for successful queries in \p\ networks.
The table below outlines how the $3$ strategies fare:
%%
\begin{center}
{\footnotesize
\begin{tabular}{rccc}
\multicolumn{1}{r}{} &
\multicolumn{1}{c}{\emph{Efficiency}} &
\multicolumn{1}{c}{\emph{Overhead}} &
\multicolumn{1}{c}{\emph{Scalability}}
\\
\cline{2-4}
\emph{Uniform Replication} &
% Proportional and Uniform are the worst “reasonable” strategies
low &
% When item is created, replicate its key in a fixed number of hosts.
low &
%
medium \\
\emph{Proportional Replication} &
% Proportional and Uniform are the worst “reasonable” strategies
low &
% for each query, replicate the key in a fixed number of hosts (need to know or
% estimate the query rate)
medium &
%
low \\
\emph{Square Root Replication Allocation} &
% All (strictly) in-between strategies are (strictly) better than Uniform and
% Proportional - replication theory
medium &
% Assuming that each query keeps track of the search size then each time a query
% is finished the object is copied to a number of sites proportional to the
% number of probes that the search required.
medium &
% e.g. path replication is easy to scale, just detect the path along which the
% query ultimately got fulfilled
medium \\
\end{tabular}
}
\end{center}

@@

Along with {\sl Narada}, the \emph{Adaptive Overlay Topology 
Optimization (AOTO)}~\cite{LZXN2003} is one of the first attempts to address the
topology mismatch problem. \emph{AOTO} is a distributed algorithm that seeks to
optimize the usage of the underlying physical resources and operates in
$2$ phases:
\emph{Selective Flooding} and \emph{Active Topology}.
In \emph{Selective Flooding}, a minimum spanning tree is built for each peer and
its immediate neighbors so that queries do not flood the entire network and at
the same time preventing their search scope from shrinking. This way some
neighbors become non--flooding. During \emph{Active Topology}, each peer
replaces independently such non--flooding neighbors, with closer nodes as an attempt
to revise the overlay links so that they can reflect more closely the physical
network topology. Picking a replacement out of these non-flooding
neighbors follows a random policy called \emph{Randomized AT} algorithm.
To accomplish the above actions, a peer has to keep track of 
its communication costs with all its neighbors (e.g., network delays)
as well as the costs between any pair of neighbors. The \emph{randomized AT}
algorithm is applied by a source peer
every time its neighbor list is updated or an updated neighbor cost 
table is received.
%%
%\paragraph*{Selective Flooding (SF)}
%
% TODO: I DON'T REMEMBER WHY THE FOLLOWING IS MENTIONING LTM WHICH IS ANOTHER
%       ALGORITM. MAYBE THIS CAN BE USED AS A PART OF DISCUSSION AND/OR
%       COMPARISON OF AOTO AND LTM
% TODO: EDIT: LTM SEEMS A MISTAKE HERE BETTER NOT USE IT FOR DISCUSSION (THIS
%             IS AOTO)
%LTM's SF effectiveness has be proven to be detached from the different physical
% or overlay topologies. On the other hand, SF is more effective with large
%number of logical neighbors. It can reach an average optimization rate of 87.4
%percent on a logical topology with an average of 30 logical neighbors.
%
%\paragraph*{Active Topology (AT)}
%
%Different numbers of average logical neighbors has little to do with the
% effectiveness of AT. If the source has $n$ non-flooding peers, there are $n$
%potential neighbor replacements. The overhead to exhaust all $n$ possible
%replacements can be high, so in practice, after each replacement the source
%peer can decide whether it needs to find another candidate peer. This is done
%by computing the cost improvement ratio greater than some predefined
%termination threshold. The larger the threshold, the slower, in the number of
%optimization steps, the reduction of the normalized average distance. As a
%whole the average response time is significantly reduced when more optimization
%steps taken.
%%
\emph{AOTO}'s performance regarding the $3$ criteria is as follows:
%%
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
%
medium &
% tracking of communication costs to all peer's neighbors as well as between
% any pair of neighbors. Whenever a new neighbor cost table is received or
% there is a change of neighbors, the source peer has to re-calculate the
% multicast tree and apply the randomized AT algorithm.
high &
% needs global knowledge
medium
\end{tabular}
}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{Adaptive Connection Establishment (ACE)}
The \emph{Adaptive Connection Establishment (ACE)} 
approach~\cite{LZXN2004} uses the network delay as a metric 
to estimate the costs between nodes. Each peer computes the costs to its
logical one-hop neighbors and forms a \emph{neighbor cost table (NCT)} 
using a special routing message type. 
Any pair of neighboring peers exchange their \emph{NCT}s 
and so a minimal overlay topology can be formed. Based on the obtained
\emph{NCT}s a minimum spanning tree for each peer and its one-hop neighbors is
created. Finally, neighbors located physically far away 
are replaced by physically-closer counterparts. 
In particular, a peer $S$ iteratively probes the distance $d$ between
itself and every of its non-flooding neighbor nodes $G$ as well as
the distance between $S$ and $G$'s neighbors designated as $H$.
If $d_{SG} > d_{SH}$, then link $SG$ is replaced by link $SH$. If, on the other
hand, $d_{SG} < d_{SH}$ then also $d_{GH}$ and then we have the following
options. Either $d_{SH} < d_{GH}$ in which case link $SH$ is kept or
$d_{SH} > d_{GH}$ in which case $S$ will keep probing other $G$'s direct
neighbors.
%%%
The above optimization is conducted within $1$-neighbor
closure using as base, a peer and checking all its direct neighbors.
Evidently the scope of such an operation could be extended.
Should  a larger scope be used, a better topology matching can be obtained 
at a greater computational overhead.
%
% TODO: SOME DISCUSSION
%
%Simulations in \cite{liu_acesims_2004} show that the average scope of each
% query to cover the same scope of nodes is reduced by about 65 percent without
%losing any autonomy feature, while the average response time can be reduced by
%35 percent. Larger diameter topologies lead to better topology optimization
%rate but also to higher communication and computation overhead. It was also
%found that it is more effective in higher connectivity dense topologies.
%Compared to LTM, it comes short of convergence speed. In
%\cite{ni_mismatch_2004} shows reduction of both total traffic (90 percent) and
%response time (80 percent) to message queries without shrinking the search
%scope.Last but
%not least, it is concluded that work must be done on incorporating a more
%sophisticated selection policy for candidate non-flooding peers.
%

%In \emph{Adaptive Connection Establishment (ACE)} \cite{LZXN2004}, the
%authors extend the idea of AOTO by introducing optimizations based on the
%depths of the minimum spanning trees. But since the network delay is not
%always a reliable estimation method to detect the physical location of peers,
%the algorithm still suffers from the discrepancies caused by mis-located nodes.
%%
%%
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% compared to LTM it has slow convergence speed.
medium &
% A little bit better that AOTO since the computation here is done within a
% certain diameter from the source peer
medium &
% Larger diameter topologies lead to better topology optimization
% rate but also to higher communication and computation overhead.
medium
\end{tabular}
}
\end{center}

@@

\emph{Location-aware Topology Matching (LTM)}~\cite{LLXNZ2004} 

@@

As seen above, the method is fully distributed and needs only minimum knowledge
of, at most, a $2$-hop distant peers. This makes it a good candidate for big
overlay networks. Also topology adaptation helps construct a well fit overlay
network with restect to the underlying one (at least with respect to network
distances). Morever will-cut list and distance cache (which stores already
probed peers) minimize the unnecessary messages for the network maintenance.
These characteristics are depicted to the $3$ evaluation criteria we use in this
survey as follows:

@@

All methods target in exposing the locality of the basic functions of the
BitTorrent protocol. Even though they do not restructure the network to map
better to the underlying infrastructure they favour the intra-AS communication
over inter-AS communication thus reducing the general cost of communication.

>>>>

The \emph{directed BFS}
tries to avoid the aforementioned delay by forwarding 
query messages only to a selected subset of available neighbors. The selection
criteria varies, from the number of results received previously or the distance
in terms of hops traveled to locate these results, to the bandwidth, or the
query load of the neighbor. That way, fewer nodes are visited but quality of
query responses is maintained, to a large degree, on the premise that the
selected heuristics can direct the search to the right path.
%
In \emph{local indices},
each node indexes data within a radius of $r$ hops and uses 
this local index to answer queries % on behalf of them 
without generating additional traffic. Local indices
greatly reduce the aggregate bandwidth usage of the network and 
improve query efficiency. However, updating such indices in 
the presence of frequent node joins/departures 
may introduce significant overhead should the radius is kept broad.
%%
Below, we outline how the techniques in~\cite{YG-M2002}
fare against the $3$ major performance criteria 
of Section~\ref{section:background}.
% \begin{center}
% \begin{tabular}{ccc}
% \textbf{Efficiency} & \textbf{Overhead} & \textbf{Scalability} \\
% \hline
% Iterative Deepening & ? & ? & ?
% Directed BFS & ? & ? & ?
% Local Indices & ? & ? & ?
% \end{tabular}
% \end{center}
\begin{center}
{\footnotesize
\begin{tabular}{rccc}
\multicolumn{1}{r}{} &
\multicolumn{1}{c}{\emph{Efficiency}} &
\multicolumn{1}{c}{\emph{Overhead}} &
\multicolumn{1}{c}{\emph{Scalability}}
\\
\cline{2-4}
\emph{Iterative Deepening} &
% needs recalculation in every iteration step
% extra delay imposed in a high churn environment that prohibits the algorithm
% to start from the last level of nodes and results in a restart of the whole
% process.
low &
% the process in not started from the beginning at each iteration step. For
% popular files this can substantially reduce overhead but for less popular
% ones, its performance might be uncertain due to the repeated restart of
% flooding
low &
% 
medium \\
\emph{Directed BFS} &
% Better time to satisfaction compared to iterative deepening
medium &
% Better quality and quicker results mean more aggregate bandwidth and
% processing power needs to be consumed since more nodes are involved (death
% spiral).
medium &
% BFS is Gnutella's non efficient communication method
medium \\
\emph{Local Indices} &
% efficiency is enhanced greatly since data pointers are replicated across the
% network
high &
% updating indices is a time and resource consuming process.
medium &
% the scalability is constrained by the indices update in a highly dynamic
% environment (high churn)
medium \\
\end{tabular}
}
\end{center}

@@

The key objective of the {\sl Gia} system~\cite{CRBLS2003} is 
to help alleviate the scalability omnipresent
in unstructured \p\ file-sharing systems.
At first, {\sl Gia} replaced {\sl Gnutella}'s blind flooding 
with random walks.
Although this adoption was 
a step in the right direction \cite{LCCLS2002},
issuing a single copy of the query within the network
effectively reduces the search scope and may negatively affect 
the success rate of the query in question.
To overcome this limitation, {\sl Gia} introduces
a token-based flow control mechanism 
that gradually redirects queries to nodes which are more
likely to answer. This flow control mechanism also helps prevent node
overloading as each peer ``announces'' the number of query requests it 
can handle, in terms of tokens, to its neighbors; to this end, 
peers only forward query requests to nodes that they previously
received tokens from. Further refinement to the search mechanism is the
support for \emph{one--hop replication} of pointers to content.
{\sl Gia} also acknowledges the heterogeneity in peer bandwidth,
processing power, disk speed, etc., of \p\ nodes and uses this
information when connecting nodes to each other.
By using a topology adaptation algorithm, 
{\sl Gia} places low capacity nodes within 
short proximity to peers with high performance features.
This topology adaptation algorithm is based on the metric 
each node maintains about its satisfaction --ranging between $0$ and $1$--
for the neighbors it finds itself associated with. 
Through message exchange, a peer can establish new connections 
or drop superseded ones in order to improve its satisfaction.
Despite the fact that {\sl Gia}'s topology adaptation algorithm 
that primarily focuses on the satisfaction of peers improves the network's 
scalability it falls short in addressing the mismatch problem
as considerations for the underlying network are not handled in explicit
terms \cite{LXLNZ2005}. Moreover it reduces the search scope, exhibits poor
performance in the worst case when matching data is not found quickly
\cite{PR2004,HJ2004} and can potentially build  disconnected topoloagies
\cite{MBL2006}.
%
In terms of the $3$ stated criteria, {\sl Gia}'s approach is as follows:
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% Reduces the search scope.
medium &
% Only one copy of the query is issued to the network.
% A token based flow control mechanism redirects queries to nodes that are most
% likely to fulfill them.
low &
% Even thought the low overhead scalability is reduced by the reducing of
% search scope.
medium
\end{tabular}
}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{Distributed Cycle Minimization Protocol (DCMP)}
Another problem with topology unaware
systems is the duplication of messages due to cycles in the network graph.
Interestingly, such cycles appear even along the correct forwarding path.
\cite{ZKB2008} focuses on this exact deficiency of overlay networks and
introduces the \emph{Distributed Cycle Minimization Protocol
(DCMP)}, a dynamic, fully distributed method that removes cycles;
this is accomplished without sacrificing
overlay connectivity, resilience and other key properties of unstructured
\p\ architectures and by avoiding a hierarchical organization of peers. 
Once a cycle is detected in {\it DCMP}, the most powerful node in that cycle 
is elected as the \emph{Gate Peer} and the cycle is then broken in that place
that it will result in the minimization of the distance between the
\emph{Gate Peer} and all other nodes that are currently part of the cycle. 
This process is managed by using two specialized message types 
namely, \emph{Information Collection Message (ICM)} and \emph{Cut Message (CM)}. 
\emph{DCMP} bases its operation on messages whose travel is limited by an
imposed $TTL$ value (max set to $7$ for most cases). This inherently limits
the protocol in detecting cycles that span for more than $TTL$ nodes.
Even though cycle elimination does improve network performance, 
it cannot  directly contribute to the solution of the topology mismatch
problem, while its perfomance in a high traffic and churn environments and its
ability to retain important characteristics of a Gnutella-like topology (i.e.,
like degree distribution, average peer distance, diameter e.t.c.) has been
doubted \cite{SCG2009,CSG2010}. On the other hand, even though some of the overhead
saved by the dublicate message reduction is spent to control the cycle cutting
mechanism it is reported that still stays for example one to two orders of
magnitude less than LTM due to its ``lazy'' broadcasting of control messages
(as opposed to LTM's periodic approach) \cite{ZKB2008}.
%
%\begin{figure}
%\centering
%  \includegraphics[scale=0.4]{img/dcmp.jpeg}
%\caption{Cycle elimination methods in DCMP}
%\label{figure:dcmp}
%\end{figure}
%
% TODO: SOME DISCUSSION
%Actually, the duplicate packet problem seems to hurt more the active nodes;
%those with higher capacities and bandwidth that contribute the most to the
%network.
The expected \emph{DCMP} behavior as far as our $3$ criteria is:
%
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% It returns more result than LTM according to experiments in
% \cite{ZKB2008}
medium &
% Duplicates are an important fraction of the redundant overhead imposed by
% topology mismatch and thus DCMP minimizes this as possible.
low &
% fully distributed method
high
\end{tabular}
}
\end{center}

@@

In \cite{CS2002} and \cite{LCCLS2002}, replication is used as a way to improve
inefficient blind search. The observation is that as the number of replicas
increases in the network, it would be relatively easy to locate items even if
search is random.

The work discusses $3$ approaches for replication allocation namely \emph{uniform},
\emph{proportional}, and \emph{square-root replication}. In the uniform model,
all objects are replicated without taking into account the query distribution,
while in the proportional, objects are replicated analogously to their query
rate, so that frequently queried items can be found more often. Experimental
outcomes indicate that the uniform allocation minimizes the maximum search
length and so it can reduce the time spent on unsuccessful searches. The
proportional strategy effectively decreases the search time for popular items,
but suffers when needing to locate the rare entities. When it comes to expected
successful search size, it is the same for for both uniform and proportional
models and any approach in between to always behave much better. Finally, the
square-root model is an attempt to find the golden ratio between uniform and
proportional allocation models. It suggests setting the number of object
replicas to the square root of the searching rate for an object\footnote{An
interesting application of the square-root principle has also been explored
in the context of topology reconstruction, by ensuring node degree to be
proportional to the square-root of its content popularity \cite{C2005}.}.
Theory in \cite{CS2002} suggest that square-root minimizes the expected search size on
successful queries, claim that is supported by simulations \cite{LCCLS2002}.

In \cite{LCCLS2002}, a \emph{k-walker} query algorithm is presented and shown
that using it along side square-root allocation results in perfomance similar to
Gnutella's query flooding method but incurring up to two
orders of magnitude less network traffic. Also checks $3$ strategies for
replica placement, namely \emph{owner replication} where an object is replicated
at the requesting node, \emph{path replication} that caches the object along the
path from the requesting to the providing node and \emph{random replication}
where the replication is taking place randomly on visited nodes. Observations in
this work are not directly applicable to structured DHTs, because it is assumed
that the lookup time for an object depends only on the number of replicas and
not the placement strategy \cite{RS2004}.

%%
%% SOME EXTRA DISCUSSION TAKEN FROM
%% IRM: Integrated File Replication and Consistency Maintenance in P2P Systems
%% 
%% Lv et al. [21] and Cohen and
%% Shenker [22] showed that replicating objects proportionally
%% to their popularity achieves optimal load balance but has
%% varied search latency, while uniform replication has the
%% same average search latency for all files but causes load
%% imbalance. Square-Root replication method replicating files
%% proportionally to the square root of their popularity is such
%% that both average search size and capacity utilization rate
%% vary per object, but the variance in utilization is consider-
%% ably smaller than with uniform replication, and the variance
%% in average search size is considerably smaller than with
%% proportional replication.
%%

The table below outlines how the $3$ allocation approaches fare:
%%
\begin{center}
{\footnotesize
\begin{tabular}{rccc}
\multicolumn{1}{r}{} &
\multicolumn{1}{c}{\emph{Efficiency}} &
\multicolumn{1}{c}{\emph{Overhead}} &
\multicolumn{1}{c}{\emph{Scalability}}
\\
\cline{2-4}
\emph{Uniform Replication} &
% Proportional and Uniform are the worst “reasonable” strategies
low &
% When item is created, replicate its key in a fixed number of hosts.
low &
%
medium \\
\emph{Proportional Replication} &
% Proportional and Uniform are the worst “reasonable” strategies
low &
% for each query, replicate the key in a fixed number of hosts (need to know or
% estimate the query rate)
medium &
%
low \\
\emph{Square Root Replication Allocation} &
% All (strictly) in-between strategies are (strictly) better than Uniform and
% Proportional - replication theory
medium &
% Assuming that each query keeps track of the search size then each time a query
% is finished the object is copied to a number of sites proportional to the
% number of probes that the search required.
medium &
% e.g. path replication is easy to scale, just detect the path along which the
% query ultimately got fulfilled
medium \\
\end{tabular}
}
\end{center}

@@

Along with {\sl Narada}, the \emph{Adaptive Overlay Topology 
Optimization (AOTO)} \cite{LZXN2003} is one of the first attempts to address the
topology mismatch problem. \emph{AOTO} is a distributed algorithm that seeks to
optimize the usage of the underlying physical resources and operates in
$2$ phases:
\emph{Selective Flooding} and \emph{Active Topology}.
In \emph{Selective Flooding}, a minimum spanning tree is built for each peer and
its immediate neighbors so that queries do not flood the entire network and at
the same time preventing their search scope from shrinking. This way some
neighbors become non--flooding. During \emph{Active Topology}, each peer
replaces independently such non--flooding neighbors, with closer nodes as an attempt
to revise the overlay links so that they can reflect more closely the physical
network topology. Picking a replacement out of these non-flooding
neighbors follows a random policy called \emph{Randomized AT} algorithm.
To accomplish the above actions, a peer has to keep track of 
its communication costs with all its neighbors (e.g., network delays)
as well as the costs between any pair of neighbors. The \emph{randomized AT}
algorithm is applied by a source peer
every time its neighbor list is updated or an updated neighbor cost 
table is received.
%%
%\paragraph*{Selective Flooding (SF)}
%
% TODO: I DON'T REMEMBER WHY THE FOLLOWING IS MENTIONING LTM WHICH IS ANOTHER
%       ALGORITM. MAYBE THIS CAN BE USED AS A PART OF DISCUSSION AND/OR
%       COMPARISON OF AOTO AND LTM
% TODO: EDIT: LTM SEEMS A MISTAKE HERE BETTER NOT USE IT FOR DISCUSSION (THIS
%             IS AOTO)
%LTM's SF effectiveness has be proven to be detached from the different physical
% or overlay topologies. On the other hand, SF is more effective with large
%number of logical neighbors. It can reach an average optimization rate of 87.4
%percent on a logical topology with an average of 30 logical neighbors.
%
%\paragraph*{Active Topology (AT)}
%
%Different numbers of average logical neighbors has little to do with the
% effectiveness of AT. If the source has $n$ non-flooding peers, there are $n$
%potential neighbor replacements. The overhead to exhaust all $n$ possible
%replacements can be high, so in practice, after each replacement the source
%peer can decide whether it needs to find another candidate peer. This is done
%by computing the cost improvement ratio greater than some predefined
%termination threshold. The larger the threshold, the slower, in the number of
%optimization steps, the reduction of the normalized average distance. As a
%whole the average response time is significantly reduced when more optimization
%steps taken.
%%
\emph{AOTO}'s performance regarding the $3$ criteria is as follows:
%%
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
%
medium &
% tracking of communication costs to all peer's neighbors as well as between
% any pair of neighbors. Whenever a new neighbor cost table is received or
% there is a change of neighbors, the source peer has to re-calculate the
% multicast tree and apply the randomized AT algorithm.
high &
% needs global knowledge
medium
\end{tabular}
}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \subsubsection{Adaptive Connection Establishment (ACE)}
The \emph{Adaptive Connection Establishment (ACE)} 
approach~\cite{LZXN2004} uses the network delay as a metric 
to estimate the costs between nodes. Each peer computes the costs to its
logical one-hop neighbors and forms a \emph{neighbor cost table (NCT)} 
using a special routing message type. 
Any pair of neighboring peers exchange their \emph{NCT}s 
and so a minimal overlay topology can be formed. Based on the obtained
\emph{NCT}s a minimum spanning tree for each peer and its one-hop neighbors is
created. Finally, neighbors located physically far away 
are replaced by physically-closer counterparts. 
In particular, a peer $S$ iteratively probes the distance $d$ between
itself and every of its non-flooding neighbor nodes $G$ as well as
the distance between $S$ and $G$'s neighbors designated as $H$.
If $d_{SG} > d_{SH}$, then link $SG$ is replaced by link $SH$. If, on the other
hand, $d_{SG} < d_{SH}$ then also $d_{GH}$ and then we have the following
options. Either $d_{SH} < d_{GH}$ in which case link $SH$ is kept or
$d_{SH} > d_{GH}$ in which case $S$ will keep probing other $G$'s direct
neighbors.
%
The above optimization is conducted within $1$-neighbor
closure using as base, a peer and checking all its direct neighbors.
Evidently the scope of such an operation could be extended.
Should  a larger scope be used, a better topology matching can be obtained 
at a greater computational overhead.
%
% TODO: SOME DISCUSSION
%
%Simulations in \cite{liu_acesims_2004} show that the average scope of each
% query to cover the same scope of nodes is reduced by about 65 percent without
%losing any autonomy feature, while the average response time can be reduced by
%35 percent. Larger diameter topologies lead to better topology optimization
%rate but also to higher communication and computation overhead. It was also
%found that it is more effective in higher connectivity dense topologies.
%Compared to LTM, it comes short of convergence speed. In
%\cite{ni_mismatch_2004} shows reduction of both total traffic (90 percent) and
%response time (80 percent) to message queries without shrinking the search
%scope.Last but
%not least, it is concluded that work must be done on incorporating a more
%sophisticated selection policy for candidate non-flooding peers.
%

%In \emph{Adaptive Connection Establishment (ACE)} \cite{LZXN2004}, the
%authors extend the idea of AOTO by introducing optimizations based on the
%depths of the minimum spanning trees. But since the network delay is not
%always a reliable estimation method to detect the physical location of peers,
%the algorithm still suffers from the discrepancies caused by mis-located nodes.
%%
%%
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% compared to LTM it has slow convergence speed because of the information
% exchange among each peer and all its neighbours.
medium &
% A little bit better that AOTO since the computation here is done within a
% certain diameter from the source peer
medium &
% Larger diameter topologies lead to better topology optimization
% rate but also to higher communication and computation overhead.
medium
\end{tabular}
}
\end{center}

@@

\emph{Location-aware Topology Matching (LTM)} \cite{LLXNZ2004}

@@

As seen above, the method is fully distributed and needs only minimum knowledge
of, at most, a $2$-hop distant peers. This makes it a good candidate for big
overlay networks. Also topology adaptation helps construct a well fit overlay
network with restect to the underlying one (at least with respect to network
distances). Morever will-cut list and distance cache (which stores already
probed peers) minimize the unnecessary messages for the network maintenance.
There are works in the literature though that critisize, through simulation
results, the algorithm's average broadcast delay and overlay improvement
guarantee \cite{HLY2010}.
These characteristics are depicted to the $3$ evaluation criteria we use in this
survey as follows:

@@

All methods target in exposing the locality of the basic functions of the
BitTorrent protocol. Even though they do not restructure the network to map
better to the underlying infrastructure they favour the intra-AS communication
over inter-AS communication thus reducing the general cost of communication.
Again, it is pointed out that there is a trade-off between reducing inter-domain
traffic and fairness among peers in terms of the data the peers upload
